Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method (EBASE)

### 2023-11-20 manu-draft.qmd
submitted

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: false
title: "Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method (EBASE)"
bibliography: refs.bib
csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Jill M Arriola:
      email: jva5648@psu.edu 
      institute: [PSU]
      correspondence: false
  - Maria Hermann:
      email: mxh367@psu.edu
      institute: [PSU]
      correspondence: false
  - Raymond G Najjar:
      email: rgn1@psu.edu
      institute: [PSU]
      correspondence: false

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: false
title: "Fitting metabolic models to dissolved oxygen data: The Estuarine BAyesian Single-station Estimation method (EBASE)"
bibliography: refs.bib
csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Jill M Arriola:
      email: jva5648@psu.edu 
      institute: [PSU]
      correspondence: false
  - Maria Herrmann:
      email: mxh367@psu.edu
      institute: [PSU]
      correspondence: false
  - Raymond G Najjar:
      email: rgn1@psu.edu
      institute: [PSU]
      correspondence: false
